Housing Market Institutions Drive Race and Ethnicity Differences in Energy Consumption

### 2015-03-18 ConferencePaper/DraftEdwardsWoods.tex
Getting the mulinom in the paper

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Sun Mar 15 22:51:59 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrrrrrrrr}
  \hline
 & FALSEWt & FALSEAfAm & FALSEAsian & FALSEMulti & FALSENativeAm & FALSEOther & FALSEPacific & TRUEAfAm & TRUEAsian & TRUEMulti & TRUENativeAm & TRUEOther & TRUEPacific & TRUEWt \\ 
  \hline
Mobile & 371 &  24 &   1 &   6 &   7 &   2 &   1 &   3 &   0 &   1 &   2 &   6 &   0 &  97 \\ 
  SFDetached & 5694 & 754 & 231 &  87 &  35 &  59 &  22 &   8 &   5 &  10 &  17 &  41 &   2 & 730 \\ 
  SFAttached & 544 & 121 &  48 &  14 &   9 &   8 &   1 &  10 &   0 &   2 &   3 &  12 &   1 & 105 \\ 
  SmApartment & 430 & 174 &  52 &  12 &   7 &  13 &   2 &   5 &   0 &   4 &   6 &  16 &   1 & 184 \\ 
  LgApartment & 951 & 382 & 113 &  27 &  15 &  29 &  10 &   8 &   1 &   4 &   9 &  24 &   0 & 332 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Race and Structure Type} 
\label{tab:RaceVStruct}
\end{table}
\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
\includegraphics{DraftEdwardsWoods-004}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Sun Mar 15 22:52:15 2015
\begin{table}[ht]
\centering
\begin{tabular}{rllr}
  \hline
 & State & Population & Reports (per 100,000) \\ 
  \hline
1 & Alabama & 4,677,464 & 7.50 \\ 
  2 & Alaska & 688,125 & 13.01 \\ 
  3 & Arizona & 6,499,377 & 3.68 \\ 
  4 & Arkansas & 2,867,764 & 9.26 \\ 
  5 & California & 36,580,371 & 3.03 \\ 
  6 & Colorado & 4,935,213 & 1.97 \\ 
  7 & Connecticut & 3,502,932 & 20.50 \\ 
  8 & Delaware & 876,211 & 14.00 \\ 
  9 & District of Columbia & 590,074 & 14.00 \\ 
  10 & Florida & 18,423,878 & 3.93 \\ 
  11 & Georgia & 9,697,838 & 2.06 \\ 
  12 & Hawaii & 1,287,481 & 13.01 \\ 
  13 & Idaho & 1,527,506 & 9.94 \\ 
  14 & Illinois & 12,842,954 & 2.88 \\ 
  15 & Indiana & 6,388,309 & 9.14 \\ 
  16 & Iowa & 2,993,987 & 19.92 \\ 
  17 & Kansas & 2,797,375 & 10.31 \\ 
  18 & Kentucky & 4,287,931 & 7.50 \\ 
  19 & Louisiana & 4,451,513 & 9.26 \\ 
  20 & Maine & 1,319,691 & 20.50 \\ 
  21 & Maryland & 5,658,655 & 14.00 \\ 
  22 & Massachusetts & 6,543,595 & 4.51 \\ 
  23 & Michigan & 10,002,486 & 4.97 \\ 
  24 & Minnesota & 5,230,567 & 19.92 \\ 
  25 & Mississippi & 2,940,212 & 7.50 \\ 
  26 & Missouri & 5,956,335 & 4.99 \\ 
  27 & Montana & 968,035 & 9.94 \\ 
  28 & Nebraska & 1,781,949 & 10.31 \\ 
  29 & Nevada & 2,615,772 & 5.08 \\ 
  30 & New Hampshire & 1,321,872 & 20.50 \\ 
  31 & New Jersey & 8,663,398 & 2.34 \\ 
  32 & New Mexico & 1,986,763 & 5.08 \\ 
  33 & New York & 19,467,789 & 4.60 \\ 
  34 & North Carolina & 9,247,134 & 4.22 \\ 
  35 & North Dakota & 641,421 & 19.92 \\ 
  36 & Ohio & 11,528,072 & 9.14 \\ 
  37 & Oklahoma & 3,644,025 & 9.26 \\ 
  38 & Oregon & 3,782,991 & 13.01 \\ 
  39 & Pennsylvania & 12,566,368 & 1.87 \\ 
  40 & Rhode Island & 1,053,502 & 20.50 \\ 
  41 & South Carolina & 4,503,280 & 4.22 \\ 
  42 & South Dakota & 804,532 & 19.92 \\ 
  43 & Tennessee & 6,240,456 & 2.61 \\ 
  44 & Texas & 24,304,290 & 4.18 \\ 
  45 & Utah & 2,727,343 & 9.94 \\ 
  46 & Vermont & 621,049 & 20.50 \\ 
  47 & Virginia & 7,795,424 & 2.03 \\ 
  48 & Washington & 6,566,073 & 13.01 \\ 
  49 & West Virginia & 1,814,873 & 14.00 \\ 
  50 & Wisconsin & 5,627,610 & 1.81 \\ 
  51 & Wyoming & 532,981 & 9.94 \\ 
   \hline
\end{tabular}
\caption{HUD Complaints per 100,000 Population} 
\label{tab:HUDComplaints}
\end{table}
\section{Conditional Demand Estimation}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Sun Mar 15 22:52:15 2015

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Sun Mar 15 22:52:15 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 1948.2943 & 80.2307 & 24.28 & 0.0000 \\ 
  RENTHELPTRUE & 206.7350 & 84.1076 & 2.46 & 0.0140 \\ 
  StrTenureOwnLgApartment & -1392.2772 & 72.2081 & -19.28 & 0.0000 \\ 
  StrTenureOwnMobile & -1134.4416 & 53.9823 & -21.02 & 0.0000 \\ 
  StrTenureOwnSFAttached & -549.6952 & 49.0434 & -11.21 & 0.0000 \\ 
  StrTenureOwnSmApartment & -779.1076 & 89.4444 & -8.71 & 0.0000 \\ 
  StrTenureRentLgApartment & -1393.4070 & 31.1855 & -44.68 & 0.0000 \\ 
  StrTenureRentMobile & -1213.4556 & 108.7993 & -11.15 & 0.0000 \\ 
  StrTenureRentSFAttached & -856.9121 & 57.0870 & -15.01 & 0.0000 \\ 
  StrTenureRentSFDetached & -553.5699 & 38.5786 & -14.35 & 0.0000 \\ 
  StrTenureRentSmApartment & -1161.1082 & 42.1556 & -27.54 & 0.0000 \\ 
  Income & 0.0078 & 0.0003 & 29.57 & 0.0000 \\ 
  reporttot & 14.8827 & 1.8850 & 7.90 & 0.0000 \\ 
  EDUCATIONNoHS & 98.3357 & 82.3383 & 1.19 & 0.2324 \\ 
  EDUCATIONHS & 109.9418 & 77.9684 & 1.41 & 0.1585 \\ 
  EDUCATIONSomeCol & 168.9859 & 78.5995 & 2.15 & 0.0316 \\ 
  EDUCATIONAA & 171.7528 & 82.0919 & 2.09 & 0.0364 \\ 
  EDUCATIONBA & 352.1423 & 79.7827 & 4.41 & 0.0000 \\ 
  EDUCATIONMA & 369.0524 & 84.7068 & 4.36 & 0.0000 \\ 
  EDUCATIONProf & 623.5784 & 105.4315 & 5.91 & 0.0000 \\ 
  EDUCATIONPHD & 499.0001 & 115.4102 & 4.32 & 0.0000 \\ 
  URUrban & -279.5002 & 25.5669 & -10.93 & 0.0000 \\ 
  reporttot:EthRaceFALSEAfAm & -4.9338 & 4.5597 & -1.08 & 0.2793 \\ 
  reporttot:EthRaceFALSEAsian & -8.7364 & 7.7372 & -1.13 & 0.2589 \\ 
  reporttot:EthRaceFALSEMulti & -18.8675 & 9.8690 & -1.91 & 0.0559 \\ 
  reporttot:EthRaceFALSENativeAm & -14.2408 & 12.0000 & -1.19 & 0.2354 \\ 
  reporttot:EthRaceFALSEOther & 0.6991 & 12.7324 & 0.05 & 0.9562 \\ 
  reporttot:EthRaceFALSEPacific & -37.5385 & 18.1475 & -2.07 & 0.0386 \\ 
  reporttot:EthRaceTRUEAfAm & -13.9581 & 28.5075 & -0.49 & 0.6244 \\ 
  reporttot:EthRaceTRUEAsian & -16.9656 & 33.5615 & -0.51 & 0.6132 \\ 
  reporttot:EthRaceTRUEMulti & 2.8707 & 16.5903 & 0.17 & 0.8626 \\ 
  reporttot:EthRaceTRUENativeAm & -22.4893 & 35.3740 & -0.64 & 0.5249 \\ 
  reporttot:EthRaceTRUEOther & 5.1444 & 11.5405 & 0.45 & 0.6558 \\ 
  reporttot:EthRaceTRUEPacific & -34.7671 & 55.4693 & -0.63 & 0.5308 \\ 
  reporttot:EthRaceTRUEWt & -23.1538 & 5.5814 & -4.15 & 0.0000 \\ 
   \hline
\end{tabular}
\caption{Orthodox Square Foot Model} 
\label{tab:OrthoSQFT}
\end{table}

>>>>

% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Wed Mar 18 09:33:26 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrrrrrrrr}
  \hline
 & FALSEWt & FALSEAfAm & FALSEAsian & FALSEMulti & FALSENativeAm & FALSEOther & FALSEPacific & TRUEAfAm & TRUEAsian & TRUEMulti & TRUENativeAm & TRUEOther & TRUEPacific & TRUEWt \\ 
  \hline
Mobile & 371 &  24 &   1 &   6 &   7 &   2 &   1 &   3 &   0 &   1 &   2 &   6 &   0 &  97 \\ 
  SFDetached & 5694 & 754 & 231 &  87 &  35 &  59 &  22 &   8 &   5 &  10 &  17 &  41 &   2 & 730 \\ 
  SFAttached & 544 & 121 &  48 &  14 &   9 &   8 &   1 &  10 &   0 &   2 &   3 &  12 &   1 & 105 \\ 
  SmApartment & 430 & 174 &  52 &  12 &   7 &  13 &   2 &   5 &   0 &   4 &   6 &  16 &   1 & 184 \\ 
  LgApartment & 951 & 382 & 113 &  27 &  15 &  29 &  10 &   8 &   1 &   4 &   9 &  24 &   0 & 332 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Race and Structure Type} 
\label{tab:RaceVStruct}
\end{table}
\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
\includegraphics{DraftEdwardsWoods-004}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Wed Mar 18 09:33:32 2015
\begin{table}[ht]
\centering
\begin{tabular}{rllr}
  \hline
 & State & Population & Reports (per 100,000) \\ 
  \hline
1 & Alabama & 4,677,464 & 7.50 \\ 
  2 & Alaska & 688,125 & 13.01 \\ 
  3 & Arizona & 6,499,377 & 3.68 \\ 
  4 & Arkansas & 2,867,764 & 9.26 \\ 
  5 & California & 36,580,371 & 3.03 \\ 
  6 & Colorado & 4,935,213 & 1.97 \\ 
  7 & Connecticut & 3,502,932 & 20.50 \\ 
  8 & Delaware & 876,211 & 14.00 \\ 
  9 & District of Columbia & 590,074 & 14.00 \\ 
  10 & Florida & 18,423,878 & 3.93 \\ 
  11 & Georgia & 9,697,838 & 2.06 \\ 
  12 & Hawaii & 1,287,481 & 13.01 \\ 
  13 & Idaho & 1,527,506 & 9.94 \\ 
  14 & Illinois & 12,842,954 & 2.88 \\ 
  15 & Indiana & 6,388,309 & 9.14 \\ 
  16 & Iowa & 2,993,987 & 19.92 \\ 
  17 & Kansas & 2,797,375 & 10.31 \\ 
  18 & Kentucky & 4,287,931 & 7.50 \\ 
  19 & Louisiana & 4,451,513 & 9.26 \\ 
  20 & Maine & 1,319,691 & 20.50 \\ 
  21 & Maryland & 5,658,655 & 14.00 \\ 
  22 & Massachusetts & 6,543,595 & 4.51 \\ 
  23 & Michigan & 10,002,486 & 4.97 \\ 
  24 & Minnesota & 5,230,567 & 19.92 \\ 
  25 & Mississippi & 2,940,212 & 7.50 \\ 
  26 & Missouri & 5,956,335 & 4.99 \\ 
  27 & Montana & 968,035 & 9.94 \\ 
  28 & Nebraska & 1,781,949 & 10.31 \\ 
  29 & Nevada & 2,615,772 & 5.08 \\ 
  30 & New Hampshire & 1,321,872 & 20.50 \\ 
  31 & New Jersey & 8,663,398 & 2.34 \\ 
  32 & New Mexico & 1,986,763 & 5.08 \\ 
  33 & New York & 19,467,789 & 4.60 \\ 
  34 & North Carolina & 9,247,134 & 4.22 \\ 
  35 & North Dakota & 641,421 & 19.92 \\ 
  36 & Ohio & 11,528,072 & 9.14 \\ 
  37 & Oklahoma & 3,644,025 & 9.26 \\ 
  38 & Oregon & 3,782,991 & 13.01 \\ 
  39 & Pennsylvania & 12,566,368 & 1.87 \\ 
  40 & Rhode Island & 1,053,502 & 20.50 \\ 
  41 & South Carolina & 4,503,280 & 4.22 \\ 
  42 & South Dakota & 804,532 & 19.92 \\ 
  43 & Tennessee & 6,240,456 & 2.61 \\ 
  44 & Texas & 24,304,290 & 4.18 \\ 
  45 & Utah & 2,727,343 & 9.94 \\ 
  46 & Vermont & 621,049 & 20.50 \\ 
  47 & Virginia & 7,795,424 & 2.03 \\ 
  48 & Washington & 6,566,073 & 13.01 \\ 
  49 & West Virginia & 1,814,873 & 14.00 \\ 
  50 & Wisconsin & 5,627,610 & 1.81 \\ 
  51 & Wyoming & 532,981 & 9.94 \\ 
   \hline
\end{tabular}
\caption{HUD Complaints per 100,000 Population} 
\label{tab:HUDComplaints}
\end{table}
\section{Conditional Demand Estimation}

@@

% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Wed Mar 18 09:33:32 2015

@@

% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Wed Mar 18 09:33:32 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 1948.2943 & 80.2307 & 24.28 & 0.0000 \\ 
  RENTHELPTRUE & 206.7350 & 84.1076 & 2.46 & 0.0140 \\ 
  StrTenureOwnLgApartment & -1392.2772 & 72.2081 & -19.28 & 0.0000 \\ 
  StrTenureOwnMobile & -1134.4416 & 53.9823 & -21.02 & 0.0000 \\ 
  StrTenureOwnSFAttached & -549.6952 & 49.0434 & -11.21 & 0.0000 \\ 
  StrTenureOwnSmApartment & -779.1076 & 89.4444 & -8.71 & 0.0000 \\ 
  StrTenureRentLgApartment & -1393.4070 & 31.1855 & -44.68 & 0.0000 \\ 
  StrTenureRentMobile & -1213.4556 & 108.7993 & -11.15 & 0.0000 \\ 
  StrTenureRentSFAttached & -856.9121 & 57.0870 & -15.01 & 0.0000 \\ 
  StrTenureRentSFDetached & -553.5699 & 38.5786 & -14.35 & 0.0000 \\ 
  StrTenureRentSmApartment & -1161.1082 & 42.1556 & -27.54 & 0.0000 \\ 
  Income & 0.0078 & 0.0003 & 29.57 & 0.0000 \\ 
  reporttot & 14.8827 & 1.8850 & 7.90 & 0.0000 \\ 
  EDUCATIONNoHS & 98.3357 & 82.3383 & 1.19 & 0.2324 \\ 
  EDUCATIONHS & 109.9418 & 77.9684 & 1.41 & 0.1585 \\ 
  EDUCATIONSomeCol & 168.9859 & 78.5995 & 2.15 & 0.0316 \\ 
  EDUCATIONAA & 171.7528 & 82.0919 & 2.09 & 0.0364 \\ 
  EDUCATIONBA & 352.1423 & 79.7827 & 4.41 & 0.0000 \\ 
  EDUCATIONMA & 369.0524 & 84.7068 & 4.36 & 0.0000 \\ 
  EDUCATIONProf & 623.5784 & 105.4315 & 5.91 & 0.0000 \\ 
  EDUCATIONPHD & 499.0001 & 115.4102 & 4.32 & 0.0000 \\ 
  URUrban & -279.5002 & 25.5669 & -10.93 & 0.0000 \\ 
  reporttot:EthRaceFALSEAfAm & -4.9338 & 4.5597 & -1.08 & 0.2793 \\ 
  reporttot:EthRaceFALSEAsian & -8.7364 & 7.7372 & -1.13 & 0.2589 \\ 
  reporttot:EthRaceFALSEMulti & -18.8675 & 9.8690 & -1.91 & 0.0559 \\ 
  reporttot:EthRaceFALSENativeAm & -14.2408 & 12.0000 & -1.19 & 0.2354 \\ 
  reporttot:EthRaceFALSEOther & 0.6991 & 12.7324 & 0.05 & 0.9562 \\ 
  reporttot:EthRaceFALSEPacific & -37.5385 & 18.1475 & -2.07 & 0.0386 \\ 
  reporttot:EthRaceTRUEAfAm & -13.9581 & 28.5075 & -0.49 & 0.6244 \\ 
  reporttot:EthRaceTRUEAsian & -16.9656 & 33.5615 & -0.51 & 0.6132 \\ 
  reporttot:EthRaceTRUEMulti & 2.8707 & 16.5903 & 0.17 & 0.8626 \\ 
  reporttot:EthRaceTRUENativeAm & -22.4893 & 35.3740 & -0.64 & 0.5249 \\ 
  reporttot:EthRaceTRUEOther & 5.1444 & 11.5405 & 0.45 & 0.6558 \\ 
  reporttot:EthRaceTRUEPacific & -34.7671 & 55.4693 & -0.63 & 0.5308 \\ 
  reporttot:EthRaceTRUEWt & -23.1538 & 5.5814 & -4.15 & 0.0000 \\ 
   \hline
\end{tabular}
\caption{Orthodox Square Foot Model} 
\label{tab:OrthoSQFT}
\end{table}

\begin{Schunk}
\begin{Soutput}
# weights:  290 (252 variable)
initial  value 27412.275532 
iter  10 value 18277.849872
iter  20 value 16456.709264
iter  30 value 15328.790711
iter  40 value 14953.228502
iter  50 value 14605.498292
iter  60 value 14072.205160
iter  70 value 13614.076441
iter  80 value 13476.010708
iter  90 value 13353.307788
iter 100 value 13165.327630
final  value 13165.327630 
stopped after 100 iterations
\end{Soutput}
\begin{Soutput}
Call:
multinom(formula = StrTenure ~ RENTHELP + TOTSQFT_EN + Income + 
    NHSLDMEM + reporttot + EDUCATION + reporttot + reporttot:EthRace + 
    UR, data = RECS)

Coefficients:
                (Intercept) RENTHELPTRUE    TOTSQFT_EN        Income
OwnLgApartment   -1.4012045    2.1454443 -0.0019509345  3.459254e-06
OwnMobile         1.8481044   -0.3335909 -0.0024782727 -1.036208e-05
OwnSFAttached    -3.6710529    0.2236006 -0.0004030778  7.180833e-07
OwnSmApartment   -3.1672555    4.6166536 -0.0010380324  2.974365e-06
RentLgApartment   1.7899438    5.1034563 -0.0030038175 -1.046446e-05
RentMobile        1.9786892    5.8969739 -0.0038888400 -3.639383e-05
RentSFAttached   -2.3878420    4.7618232 -0.0012446232 -1.021858e-05
RentSFDetached   -1.5726891    2.8200895 -0.0005734065 -1.226262e-05
RentSmApartment   0.1807821    5.1008582 -0.0026323099 -1.619186e-05
                   NHSLDMEM    reporttot EDUCATIONNoHS EDUCATIONHS
OwnLgApartment  -0.34797258  0.015013718   0.477269446  0.37401861
OwnMobile        0.15128116 -0.004738898   0.485162185  0.11640843
OwnSFAttached   -0.25038723  0.008050993   0.226793906  0.85684652
OwnSmApartment  -0.28237646 -0.009663942  -0.688673023 -0.03748283
RentLgApartment -0.03500606  0.011237582   0.004987983 -0.04286051
RentMobile       0.40934677 -0.051218671   0.390739477  0.14594218
RentSFAttached   0.12059529  0.034419469  -0.030921130 -0.23572032
RentSFDetached   0.30723498  0.001014244   0.102122854 -0.01403466
RentSmApartment  0.05205921 -0.014265982   0.263488737  0.02949444
                EDUCATIONSomeCol EDUCATIONAA EDUCATIONBA EDUCATIONMA
OwnLgApartment         0.6929779  0.65737452  0.95739291   1.4417718
OwnMobile              0.7905695  0.21659624 -0.35389397  -1.6492500
OwnSFAttached          0.8985078  0.87238180  1.52406591   1.2864582
OwnSmApartment        -0.3374229 -0.16358571  0.11573260  -0.4165630
RentLgApartment        0.2805560  0.27019330  0.66607255   0.7373567
RentMobile            -0.2202073  0.00850999 -1.06151061  -5.7933615
RentSFAttached         0.2031599 -0.13171082  0.02641089  -0.1009914
RentSFDetached         0.2157358  0.11563920 -0.10035484  -0.4337383
RentSmApartment        0.3623767  0.41090394  0.47854431   0.1297479
                EDUCATIONProf EDUCATIONPHD    URUrban
OwnLgApartment      1.8736513    1.2372782  1.4520879
OwnMobile          -2.1151470   -2.4556028 -1.1014520
OwnSFAttached       1.5983874    1.5419624  1.6277862
OwnSmApartment      0.3985125    0.5267079  2.3226177
RentLgApartment     0.9433553    0.9234813  1.5801513
RentMobile          1.7018720    2.9972013 -1.0603773
RentSFAttached     -0.8478266    0.4381929  1.9708629
RentSFDetached     -0.1725402   -0.0787602  0.5626279
RentSmApartment     0.3681771    0.6908721  1.9187057
                reporttot:EthRaceFALSEAfAm reporttot:EthRaceFALSEAsian
OwnLgApartment                -0.061129933                  0.07766379
OwnMobile                     -0.253501612                 -0.71539058
OwnSFAttached                  0.073028129                  0.06828815
OwnSmApartment                -0.003398508                 -0.07136701
RentLgApartment                0.135654877                  0.06161987
RentMobile                    -0.584744072                 -1.76876817
RentSFAttached                 0.135991827                 -0.04106818
RentSFDetached                 0.075353177                 -0.00935299
RentSmApartment                0.190626173                  0.12929070
                reporttot:EthRaceFALSEMulti reporttot:EthRaceFALSENativeAm
OwnLgApartment                 -0.218513213                   -0.542488392
OwnMobile                       0.009344288                    0.026094924
OwnSFAttached                  -0.024491876                    0.079630580
OwnSmApartment                 -0.260290488                   -0.551033411
RentLgApartment                 0.097746978                    0.029581017
RentMobile                     -0.615016447                   -0.036504716
RentSFAttached                  0.014477356                    0.092926422
RentSFDetached                  0.093122527                   -0.017882116
RentSmApartment                 0.037601924                   -0.002009332
                reporttot:EthRaceFALSEOther reporttot:EthRaceFALSEPacific
OwnLgApartment                  -0.02561634                   -0.68676247
OwnMobile                       -0.55227399                   -0.04961086
OwnSFAttached                   -0.02252647                   -5.15650607
OwnSmApartment                  -0.13826734                   -1.70662972
RentLgApartment                  0.05565783                    0.10232812
RentMobile                      -0.01394297                   -2.42342974
RentSFAttached                   0.11273668                   -1.10930205
RentSFDetached                   0.05107721                    0.01030506
RentSmApartment                  0.07408486                   -0.25631938
                reporttot:EthRaceTRUEAfAm reporttot:EthRaceTRUEAsian
OwnLgApartment               -0.994558317                -0.33037417
OwnMobile                    -0.008599062                -0.49712877
OwnSFAttached                 0.901421947                -1.07591077
OwnSmApartment                0.720621562                -0.42752187
RentLgApartment               0.702580769                -0.08253460
RentMobile                    0.823029357                -0.71191633
RentSFAttached                0.706637515                -1.72623591
RentSFDetached                0.653334007                 0.04942301
RentSmApartment               0.779288301                -2.09522007
                reporttot:EthRaceTRUEMulti reporttot:EthRaceTRUENativeAm
OwnLgApartment                 -0.19864986                     0.4914334
OwnMobile                       0.03562188                     0.2623866
OwnSFAttached                  -1.13148003                     0.3121788
OwnSmApartment                  0.17970443                     0.4218565
RentLgApartment                 0.14034061                     0.3174522
RentMobile                      0.21249252                    -0.5517922
RentSFAttached                 -0.81366313                     0.4200183
RentSFDetached                  0.03562691                     0.1682046
RentSmApartment                 0.31811515                     0.3544462
                reporttot:EthRaceTRUEOther reporttot:EthRaceTRUEPacific
OwnLgApartment                  0.02180558                 -0.397523801
OwnMobile                      -0.06062417                 -0.180497351
OwnSFAttached                   0.03002728                  0.281796703
OwnSmApartment                  0.18705769                  0.142528296
RentLgApartment                 0.07142922                 -1.524863739
RentMobile                      0.21052647                 -1.033877065
RentSFAttached                  0.07825611                 -0.689753196
RentSFDetached                 -0.06288220                 -3.109386196
RentSmApartment                 0.08111029                 -0.004257285
                reporttot:EthRaceTRUEWt
OwnLgApartment              -0.07852315
OwnMobile                   -0.03453491
OwnSFAttached               -0.02259886
OwnSmApartment              -0.05248278
RentLgApartment              0.04717723
RentMobile                  -0.01815809
RentSFAttached               0.01876969
RentSFDetached               0.03145875
RentSmApartment              0.08247824

Std. Errors:
                 (Intercept) RENTHELPTRUE   TOTSQFT_EN       Income
OwnLgApartment  4.351724e-08 1.361833e-10 8.042083e-05 1.486828e-06
OwnMobile       4.801794e-08 2.878315e-11 7.351840e-05 2.004093e-06
OwnSFAttached   1.093224e-08 2.331910e-11 3.658997e-05 1.015700e-06
OwnSmApartment  3.405954e-08 1.684418e-09 8.323208e-05 1.893700e-06
RentLgApartment 3.217775e-08 1.259582e-08 4.426271e-05 1.009244e-06
RentMobile      1.680366e-07 2.380603e-08 1.954323e-04 6.852449e-06
RentSFAttached  2.662972e-08 3.695408e-09 5.604870e-05 1.623214e-06
RentSFDetached  2.296883e-08 1.271973e-09 3.053730e-05 1.052931e-06
RentSmApartment 4.160313e-08 6.682058e-09 5.994973e-05 1.579855e-06
                    NHSLDMEM    reporttot EDUCATIONNoHS  EDUCATIONHS
OwnLgApartment  8.500718e-08 3.075767e-07  4.870920e-09 1.386252e-08
OwnMobile       1.299624e-07 3.006569e-07  1.355709e-08 1.767290e-08
OwnSFAttached   2.393908e-08 7.985562e-08  9.307634e-10 3.961343e-09
OwnSmApartment  7.270828e-08 2.359306e-07  3.187754e-09 1.477896e-08
RentLgApartment 8.193668e-08 2.062674e-07  1.301925e-08 1.208165e-08
RentMobile      5.537054e-07 9.511767e-07  7.046973e-08 6.631369e-08
RentSFAttached  7.665648e-08 2.069790e-07  6.389055e-09 9.143159e-09
RentSFDetached  1.007340e-07 1.130154e-07  1.170572e-08 7.680150e-09
RentSmApartment 1.102293e-07 2.587058e-07  1.173288e-08 1.497742e-08
                EDUCATIONSomeCol  EDUCATIONAA  EDUCATIONBA  EDUCATIONMA
OwnLgApartment      1.158332e-08 4.914648e-09 5.566968e-09 2.329809e-09
OwnMobile           1.491993e-08 2.521968e-09 4.256616e-10 3.059156e-11
OwnSFAttached       2.523770e-09 1.061512e-09 2.194114e-09 4.833421e-10
OwnSmApartment      6.977600e-09 3.697818e-09 4.241222e-09 6.433379e-10
RentLgApartment     7.959396e-09 2.991435e-09 3.372193e-09 3.581167e-10
RentMobile          1.813836e-08 5.950328e-09 7.252824e-11 9.122272e-13
RentSFAttached      7.476959e-09 1.936084e-09 1.891315e-09 2.454978e-10
RentSFDetached      3.744902e-09 9.586280e-10 1.326644e-09 3.522232e-10
RentSmApartment     1.017352e-08 3.547218e-09 2.200330e-09 1.212453e-10
                EDUCATIONProf EDUCATIONPHD      URUrban
OwnLgApartment   1.264854e-10 1.966242e-10 3.914011e-08
OwnMobile        1.174724e-11 1.327710e-11 2.054870e-08
OwnSFAttached    1.626516e-10 6.605900e-11 9.742949e-09
OwnSmApartment   1.079404e-10 1.247334e-10 3.236071e-08
RentLgApartment  2.764815e-10 7.535749e-10 2.760945e-08
RentMobile       5.514256e-10 1.506763e-09 9.058000e-08
RentSFAttached   1.052140e-11 9.127383e-11 2.471527e-08
RentSFDetached   6.977103e-11 2.535682e-11 1.538717e-08
RentSmApartment  4.023520e-11 1.231473e-10 3.864537e-08
                reporttot:EthRaceFALSEAfAm reporttot:EthRaceFALSEAsian
OwnLgApartment                1.963367e-08                5.606453e-09
OwnMobile                     1.362978e-08                1.615299e-11
OwnSFAttached                 9.815614e-09                1.350058e-09
OwnSmApartment                1.921235e-08                2.132416e-10
RentLgApartment               4.541580e-08                2.210217e-09
RentMobile                    1.942309e-08                7.827963e-12
RentSFAttached                4.187071e-08                9.156847e-10
RentSFDetached                1.910479e-08                2.239577e-09
RentSmApartment               7.118139e-08                4.919406e-09
                reporttot:EthRaceFALSEMulti reporttot:EthRaceFALSENativeAm
OwnLgApartment                 2.615273e-10                   9.367484e-11
OwnMobile                      4.200240e-09                   6.379168e-09
OwnSFAttached                  2.550073e-10                   1.109178e-09
OwnSmApartment                 1.935621e-10                   5.739529e-11
RentLgApartment                4.251619e-09                   2.523858e-09
RentMobile                     1.011654e-09                   1.426604e-08
RentSFAttached                 1.781757e-09                   4.230313e-09
RentSFDetached                 2.187221e-09                   1.898748e-09
RentSmApartment                2.506901e-09                   1.606973e-09
                reporttot:EthRaceFALSEOther reporttot:EthRaceFALSEPacific
OwnLgApartment                 1.090309e-09                  2.227915e-11
OwnMobile                      8.697048e-11                  1.698262e-09
OwnSFAttached                  2.490790e-10                  2.558331e-16
OwnSmApartment                 1.256503e-10                  6.267601e-13
RentLgApartment                1.880471e-09                  9.010899e-10
RentMobile                     3.482380e-09                  2.806748e-13
RentSFAttached                 6.042252e-09                  2.639569e-12
RentSFDetached                 2.204181e-09                  3.601196e-10
RentSmApartment                2.452424e-09                  1.655045e-11
                reporttot:EthRaceTRUEAfAm reporttot:EthRaceTRUEAsian
OwnLgApartment               1.200681e-12               3.770832e-11
OwnMobile                    8.285815e-10               4.408003e-11
OwnSFAttached                2.950472e-10               4.674004e-13
OwnSmApartment               7.533099e-10               1.311664e-11
RentLgApartment              7.302695e-09               1.623169e-10
RentMobile                   2.160392e-08               2.622579e-10
RentSFAttached               2.013095e-09               3.157614e-13
RentSFDetached               5.062913e-09               1.471258e-10
RentSmApartment              5.034675e-09               3.440708e-13
                reporttot:EthRaceTRUEMulti reporttot:EthRaceTRUENativeAm
OwnLgApartment                7.673547e-11                  7.795320e-10
OwnMobile                     1.673434e-10                  8.459745e-10
OwnSFAttached                 6.945296e-13                  1.942390e-10
OwnSmApartment                4.258973e-09                  3.941367e-10
RentLgApartment               1.115209e-09                  8.417261e-10
RentMobile                    2.474460e-09                  2.379009e-10
RentSFAttached                1.180096e-12                  8.788977e-10
RentSFDetached                2.050147e-09                  3.858355e-10
RentSmApartment               6.918216e-09                  1.286191e-09
                reporttot:EthRaceTRUEOther reporttot:EthRaceTRUEPacific
OwnLgApartment                1.562151e-09                 2.575334e-12
OwnMobile                     1.582095e-09                 2.668836e-10
OwnSFAttached                 1.052125e-09                 1.270903e-10
OwnSmApartment                2.413554e-08                 9.823655e-11
RentLgApartment               5.490875e-08                 2.399506e-14
RentMobile                    1.566813e-07                 1.182834e-12
RentSFAttached                3.278555e-08                 1.156016e-12
RentSFDetached                4.937909e-09                 5.975457e-15
RentSmApartment               2.918801e-08                 1.839679e-10
                reporttot:EthRaceTRUEWt
OwnLgApartment             1.438646e-08
OwnMobile                  3.358932e-08
OwnSFAttached              3.806993e-09
OwnSmApartment             1.043395e-08
RentLgApartment            3.496748e-08
RentMobile                 1.828711e-07
RentSFAttached             2.182158e-08
RentSFDetached             4.080229e-08
RentSmApartment            4.782485e-08

Residual Deviance: 26330.66 
AIC: 26834.66 
\end{Soutput}
\end{Schunk}
